\documentclass{letter}

\makeatletter
\newenvironment{thebibliography}[1]
     {\list{\@biblabel{\@arabic\c@enumiv}}
           {\settowidth\labelwidth{\@biblabel{#1}}
            \leftmargin\labelwidth
            \advance\leftmargin\labelsep
            \usecounter{enumiv}
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{\@arabic\c@enumiv}}
      \sloppy
      \clubpenalty4000
      \@clubpenalty \clubpenalty
      \widowpenalty4000
      \sfcode`\.\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}
      \endlist}
\newcommand\newblock{\hskip .11em\@plus.33em\@minus.07em}
\makeatother

\usepackage[utf8]{inputenc}
\usepackage{amsmath,amsthm,amsfonts,amssymb,amscd}
\usepackage[margin=0.5in,includehead]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{orcidlink}
\usepackage{bibentry}

\usepackage{xcolor}
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy} 
\setlength{\headsep}{0in}
\renewcommand{\headrulewidth}{0in}
\renewcommand{\footrulewidth}{0in}
\fancyhf{}
\fancyhead[L]{\textcolor{gray}{\thepage}}
\fancyhead[R]{\textcolor{gray}{Updated on \today}}

\newcommand{\link}[2]{
\href{#1}{\underline{\texttt{#2}}}
}

\newcommand{\section}[1]{
\Large{\textbf{\MakeUppercase{#1}}}

\vspace{-0.3in}
\rule{\textwidth}{0.25mm}
\vspace{-0.35in}
}

\newcommand{\education}[5]{
\large{\textbf{#1 \hfill #2}}

\vspace{-1.5mm}

\normalsize{#3 \hfill #4}

\vspace{-1.5mm}

\normalsize{#5}
}

\newcommand{\experience}[3]{
\large{\textbf{#1} \hfill \normalsize{#2}}

\vspace{-2.5mm}

\normalsize{#3}

\vspace{-2.5mm}
}

\begin{document}

\begin{center}
\huge{\textbf{\MakeUppercase{Yifei Sun}}} \orcidlink{0000-0002-1591-7458}

\normalsize{
\link{https://yifei.md}{yifei-s.com}
\hspace{1mm}$\mid$\hspace{1mm}
\link{mailto:yifei@email.com}{hi@yifei-s.com}
\hspace{1mm}$\mid$\hspace{1mm}
\link{https://github.com/stepbrobd}{github.com/yifei-s}
\hspace{1mm}$\mid$\hspace{1mm}
\link{https://www.linkedin.com/in/yifei-s}{linkedin.com/in/yifei-s}
}
\end{center}

\section{Education}

\education{Northeastern University}
{M. Sc. in Computer Science}
{2023/09 - 2024/12}
{Boston, MA, USA} {
Attended: PyCon 2023 (in-person), WWDC 2023 (in-person).\\
Thesis: TBD. Advisor: TBD.
}

\education{University of Utah}
{B. Sc. in Computer Science}
{2019/08 - 2023/05}
{Salt Lake City, UT, USA} {
Attended: CppCon 2021 (in-person), PyCon 2022 (in-person), DockerCon 2022 (virtual), HackMIT 2022 (in-person).\\
Thesis: Hardware System and Methods to Determine ME/CFS and Long COVID Disease Severity Using Wearable Sensor and Survey Data. Advisor: Dr. Shad Roundy. Co-advisor: Dr. Tucker Hermans.
}

\section{Experience}

\experience{Research Assistant, University of Utah}{2021/08 - 2023/05} {
\begin{itemize}
\item Joint research project advised under Dr. Shad Roundy, co-advised under Dr. Tucker Hermans, and in collaboration with the Bateman Horne Center's clinical research team, developed and managed a new data collection infrastructure.
\item The infrastructure includes 20+ embedded devices, 100+ IMUs, and multiple high-performance servers. We collected terabyte-level motion data, and performed sensor fusion and motion analysis techniques.
\item We are planning to use our research outcome to propose to medical regulators as a possible standardized diagnostic procedure and severity categorization for ME/CFS, Long COVID, and other related medical syndromes.
\end{itemize}
}

\experience{System Administrator, University of Utah}{2019/12 - 2020/09} {
\begin{itemize}
\item Enterprise system administration, managed 1000+ university-owned Apple devices (Macs, iPads, Apple TVs, etc.).
\item Utilized Jamf Pro, Radmind, and Apple School Manager to perform day-to-day MDM tasks. Created multiple automation tools to perform unattended on-boarding, off-boarding, and package distributions.
\end{itemize}
}

\experience{Intern, DJI}{2018/07 - 2018/08} {
\begin{itemize}
\item Competitive robotic system design/modeling, embedded system programming, control system programming, and computer vision. Developed path planning and task scheduling algorithms for predefined workflow.
\item Utilized STM32F4 platform to built out a robotic system with wireless image transmission, image recognition, automated reasoning, and task scheduling capabilities, following predefined rules sets to complete tasks.
\end{itemize}
}

\section{OSS Contribution}

\experience{NixPkgs}
{\link{https://github.com/nixos/nixpkgs}{github.com/nixos/nixpkgs}} {
\begin{itemize}
\item Nix Packages collection, 1000+ commits per month.
\item NixPkgs maintainer; Darwin maintainer.
\item 1 open PR, 8 closed PR, 10+ reviewed PR.
\end{itemize}
}

\experience{MetaProcessor}
{\link{https://github.com/metaprocessor/metaprocessor}{github.com/metaprocessor/metaprocessor}} {
\begin{itemize}
\item Code owner, main contributor, package published on PyPI.
\item Data collection pipeline developed for MbientLab MetaMotion series IMUs.
\item Collected 1TB+ IMU data in a joint research project in collaboration Bateman Horne Center. 
\end{itemize}
}

\section{Publication}

\normalsize{
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{publication}
}

\end{document}
